Current State of Knowledge Representation Systems for Robotics

### 2011-11-22 paper.tex
Added some content to the introduction

@@

\subsection{Definition of inclusion criteria}

We have setup the following criteria to select the knowledge representation
systems to include in this survey.

Those systems must:

@@

\subsubsection{Desired features from other fields}
\label{sect|evaluation-literature}

@@

\paragraph{Open World Assumption or Close World Assumption}

>>>>

\newcommand{\ie}{{\textit{i.e.~}}}
\newcommand{\cf}{{\textit{cf~}}}
\newcommand{\eg}{{\textit{e.g.~}}}

@@

The idea of \emph{Cognitive robotics} was coined in the early 1990s by Reiter.
In a chapter on that subject in \emph{Fondations of Artifical
Intelligence}~\cite{Levesque2007}, Levesque reminds about the manifesto they
wrote together in 1998:

\begin{quotation}

	Central to this effort is to develop an understanding of the relationship
	between the knowledge, the perception, and the action of such a robot. The
	sorts of questions we want to be able to answer are

	\begin{itemize}

		\item to execute a program, what information does a robot need to have
		at the outset vs. the information that it can acquire \emph{en route}
		by perceptual means?

		\item what does the robot need to know about its environment vs. what
		need only be known by the designer?

		\item when should a robot use perception to find out if something is
		true as opposed to reasoning about what it knows was true in the past?

		\item when should the inner workings of an action be available to the
		robot for reasoning and when should the action be considered primitive
		or atomic?

	and so on. With respect to robotics, our goal (like that of many in AI) is
	\emph{high-level robotic control}: develop a system that is capable of
	generating actions in the world that are appropriate as a function of some
	current set of beliefs and desires.

\end{quotation}

This survey focuses on the knowledge issue: we aims at establishing the current
landscape of approaches to the knowledge representation problem in the research
community.

We have identified over ten projects that are designed for explicit knowledge
manipulation within a robot. By knowledge manipulation, we mainly mean:

\begin{itemize}

	\item symbolic representation of assertions, be it static statements on the
	world or spatio-temporal events,

	\item reasoning that this representation enables,

We will also try, for each project, to make clear

\begin{itemize}

	\item how new facts can be acquired, \ie how informations from perception
	or interaction are turned into knowledge,

	\item how, in return, symbolic concept are \emph{anchored} into the robot
	sensori-motor space,

	\item how the knowledge representation system integrates with the
	decisional layers of the robot, and if this leads to better robotic
	control.

\subsection{Definition of inclusion criteria}
\label{sect|inclusion-criteria}

Every robotic system has, implicitely or not, some knowledge representation
systems. It may range from a simple state vector to an explicit symbolic
knowledge base.  This survey focuses on the right end of this spectrum:
symbolic systems, suited for abstract reasoning.

Besides, we have decided to restraint the set of systems to those actually
implemented on robots, and used in semantic-rich environments (\ie , dynamic,
partially unknown environments with a large range of different entities which
may have interactions). The typical scenario that would involve such robots is
a service robot in a human-friendly environment like a kitchen.

More precisely, we have established the following criteria to select the
knowledge representation systems to include in this survey. Those systems must:

@@

\subsubsection{Desirable features of a knowledge representation system}
\label{sect|evaluation-literature}

@@

\paragraph{Open World and Close World Assumptions}

\fixme{cf Levesque~\cite{Levesque2007}, section 24.3.2}
